Statement-level AST-based Clone Detection in Java using Resolved Symbols

### 2019-12-10 benevol/paper.tex
Working on copyright
Updates from Overleaf

\documentclass[conference]{IEEEtran}

@@

@@

@@

@@

We find that, when taking into account contextual information in our clone detection, 11\% fewer clones are found. Manually inspecting a sample of the difference, we find that they are less relevant for refactoring.
\end{abstract}

>>>>

\documentclass[journal]{IEEEtran}

@@

% \makeatletter
% \def\ps@IEEEtitlepagestyle{%
%   \def\@oddfoot{\mycopyrightnotice}%
%   \def\@evenfoot{}%
% }
% \def\mycopyrightnotice{%
%   {\hfill \footnotesize 978-1-4673-9563-2/15/\$31.00 \copyright 2015 IEEE\hfill}
% }
% \makeatother

@@

%\copyright{Copyright 2019 for this paper by its authors. Use permitted under Creative Commons License Attribution 4.0 International (CC BY 4.0).}

% \IEEEoverridecommandlockouts
% \IEEEpubid{\makebox[\columnwidth]{978-1-5386-5541-2/18/\$31.00~\copyright2018 IEEE \hfill} \hspace{\columnsep}\makebox[\columnwidth]{ bla bla}}

\newcommand\blfootnote[1]{%
  \begingroup
  \renewcommand\thefootnote{}\footnote{#1}%
  \addtocounter{footnote}{-1}%
  \endgroup
}

@@

% \IEEEpubid{\begin{minipage}{\textwidth}\ \\[12pt] \centering
%   1551-3203 \copyright 2015 IEEE. Personal use is permitted, but republication/redistribution requires IEEE permission.\\
%   See http://www.ieee.org/publications standards/publications/rights/index.html for more information.
% \end{minipage}}

% \IEEEpubidadjcol

@@

We find that, when taking into account contextual information in our clone detection, 11\% fewer clones are found. Manually inspecting a sample of the difference, we find that they are less relevant for refactoring.\blfootnote{Copyright 2019 for this paper by its authors. Use permitted under Creative Commons License Attribution 4.0 International (CC BY 4.0).}
\end{abstract}
